MaxEnt: What is it good for?

### 2015-06-19 ms.tex
john w

\section*{Acknowledgements}
It is a pleasure to thank
Ariel Caticha (Albany),
Adom Giffin (Clarkson)
John Skilling (MaxEnt Data Consultants),
Carlos Rodriguez (Albany),
Stephen Gull (Cambridge),
Kevin Knuth (Albany),
Iain Murray (Edinburgh),
Anna Pancoast (UCSB),
Geraint Lewis (Sydney),
David Hogg (NYU),
Tom Loredo (Cornell),
Daniela Huppenkothen (NYU),
Peter Tuthill (Sydney),

>>>>

\section*{Acknowledgements}
It is a pleasure to thank
Ariel Caticha (Albany),
Adom Giffin (Clarkson)
John Skilling (MaxEnt Data Consultants),
Carlos Rodriguez (Albany),
Stephen Gull (Cambridge),
Kevin Knuth (Albany),
Iain Murray (Edinburgh),
Anna Pancoast (UCSB),
Geraint Lewis (Sydney),
David Hogg (NYU),
Tom Loredo (Cornell),
Daniela Huppenkothen (NYU),
Peter Tuthill (Sydney),
and John Wilcox (Auckland)
for valuable discussions.
